Automatic conversion of colloquial Finnish to standard Finnish

### 2015-01-21 finnormal-nodalida-2015/finnormal2015.tex
some results from the unsupervised stuffs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58452 72bbbca6-d526-0410-a7d9-f06f51895060
corpus stats
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58515 72bbbca6-d526-0410-a7d9-f06f51895060

\author{Francis M. Tyers\\
  UiT Norgga \'{a}rktala\v{s} universitehta, \\
  N-9015 Norway \\
  {\tt francis.tyers@uit.no} \\\And
  Inari Listenmaa\\
  Chalmers tekniska h\"{o}gskola, \\
  Sweden \\
  {\tt inari@cse.chalmers.se} \\}

\date{}

@@

@@

\begin{itemize}
  \item 273 rules from \newcite{karlsson2008}'s grammar of Finnish (\S95--97)
  \item Rules from the development corpus.
\end{itemize}

@@

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|r|}
     \hline
    \textbf{System} & \textbf{PER} & \textbf{WER} & \textbf{BLEU} \\
     \hline
     Baseline & 46.12 & 48.04 & 26.31 \\
     \hline
     rules-1 & 38.27 & 41.19 & 32.65 \\
     rules-2 & - & - & - \\
     \hline
     CBMT-cn & - & - & - \\
     CBMT-cs & - & - & - \\
     PBMT-cn & - & - & - \\
     PBMT-cs & - & - & - \\
     \hline
  \end{tabular}
  \label{table:results}
  \caption{Results...}
\end{table}

>>>>

\author{}
%
%Francis M. Tyers\\
%  UiT Norgga \'{a}rktala\v{s} universitehta, \\
%  N-9015 Norway \\
%  {\tt francis.tyers@uit.no} \\\And
%  Inari Listenmaa\\
%  Chalmers tekniska h\"{o}gskola, \\
%  Sweden \\
%  {\tt inari@cse.chalmers.se} \\}
%
\date{}

@@

\begin{table}
  \centering
 \begin{tabular}{|l|r|}
    \hline
    \textbf{Section} & \textbf{Tokens} \\
    \hline
    \texttt{train} & 2,538 \\
    \texttt{test} & 1,012 \\
    \texttt{dev} & 1,003 \\
    \hline
 \end{tabular} 
  \caption{Statistics on sentences from the parallel corpus.}
  \label{table:corpsize}
\end{table}

@@

\begin{itemize}
  \item 273 rules from \newcite{karlsson2008}'s grammar of Finnish (\S95--97). The 
    rules took around one hour to implement.
  \item 98 rules written by examining the development corpus, these rules also
    took approximately one hour to implement.
\end{itemize}

@@

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|r|}
     \hline
    \textbf{System} & \textbf{PER} & \textbf{WER} & \textbf{BLEU} \\
     \hline
     Baseline & 46.12 & 48.04 & 26.31 \\
     \hline
     rules-1 & 38.27 & 41.19 & 32.65 \\
     rules-2 & 38.17 & 35.25 & 36.41 \\
     rules-c & 36.56 & 39.68 & 34.68 \\
     \hline
     CBMT-cn & - & - & - \\
     CBMT-cs & - & - & - \\
     PBMT-cn & - & - & - \\
     PBMT-cs & - & - & - \\
     \hline
  \end{tabular}
  \label{table:results}
  \caption{Results...}
\end{table}
